A recipe for extremely reproducible enrichment analysis

### 2023-04-13 manuscript.Rmd
Update manuscript.Rmd

* bar graph

@@

>>>>

* Bar graph

@@

Bar graph denoting the level of reproducibility of the 20 journal articles.

While going through the papers a lot of discrepancies were observed. Out of the 20 journal articles were analysed, 
thirty five percent (35%) of the papers showed low levels of reproducibility, fifty percent (50%) of the papers showed 
medium level of reproducibility and only fifteen percent (15 %) of the papers showed a high degree of reproducibility of 
the DAVID analysis results.
